Profit Optimisation in Heterogeneous 2-link Parallel Games

### 2024-12-30 thesis/article.tex
Thesis: Related Work, Chapter 3 and Examples fixes after meeting with Th. Liannea

The structure of this thesis is as such.
We finish this chapter by briefly presenting previous work in this field, all while examining some of the different models and properties that have been researched in the literature so far.
This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
This includes formal definitions of the models and properties we introduced from previous work, as well as some additional -but still basic- properties of the models, with heavy focus on the user's time-money trade-off, captured by a money-sensitivity distribution function $\alpha$.

Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-sensitivity makes them view the two links as equal.
We will then analyse that notion and provide properties and bounds for its values.
Finally, in the chapter's main result, we prove a general property of heterogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.

@@

Selfish routing has a vast history of literature as it's been proven useful in solving a variety of real-world problems in economics \cite{pigou1920economics}, transportation \cite{beckmann1956studies} and more (see \cite{roughgarden2002sr} and \cite{roughgarden2005slpoa} for more references).
It has been well-established, at least as early as 1920 from the work of Pigou \cite{pigou1920economics}, that selfish behavior in congested networks can create (arbitrary) inefficiencies with regard to the total latency experienced by all users.
A long-standing practice to solve these inefficiencies has been to regulate the network by adding tolls to the links, thus altering the cost of the link usage.
A classical result on this is the use of marginal tolls (Beckman et al. \cite{beckmann1956studies}), where each link user is charged a toll corresponding to their externality, i.e. the added congestion effect caused by their participation in the network.
This technique can eradicate the inefficiencies and create optimal flow in the network, however it assumes a strong homogeneity among the users.
Marginal cost pricing has been investigated in networks with heterogeneous users (e.g. Dafermos \cite{dafermos1973toll}), with the resulting payment required by users on same links being different, an unwanted and non-practical approach, which also requires knowledge of the users' sensitivity beforehand.

Congestion games were formally introduced by Rosenthal \cite{Rosenthal1973ACO} who also proved that in those games a pure Nash Equilibrium always exists.
Later, Monterer-Shapely \cite{MONDERER1996124} defined the class of potential games (games where the incentive for all players to change their strategy can be expressed with a global function) and proved that congestion games are equivalent to exact potential games (potential games where a change in strategy from any player alter the potential function the exact way it alters the player's cost).
One of the major contributions in this field has been the introduction of the Wardrop equilibrium \cite{wardrop_theoretical_1952}, a notion of Nash equilibrium for potential games, where the Wardrop principles provide a framework to describe and analyse those equilibria.
Milchtaich \cite{MILCHTAICH1996111} then investigated different pay-off functions for congestion games, where he showed that even though some best-reply strategies may end up in a cyclic path, there is always a path that leads to Nash equilibrium with pure strategies.

@@

In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different time-money trade-off values.
We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by a player, making them see the cost of a link with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
We call $\alpha$ a \textit{distribution function}.
Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
%Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.

@@

@@

One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money-sensitivity values, view toll values also differently, and therefore, in practice, play different games.
In the analysis of Example \ref{example:simple_alpha} we can find a first glimpse on how to tackle this issue, as we can see that the flow users on each link are organised around the player that views the two link costs as equal.
This notion will be the center of this chapter, and using it we will try and describe some properties about all users.

We start with a simple example in a network with $2$ links.
Consider $([2], \ell, \alpha)$, a heterogeneous parallel game with two links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
For the $2$ links of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player views the $2$ links' total costs as equal.
More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
from which, after solving for $\as(t)$, we get
\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\\
Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
\begin{itemize}
	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on link $1$
	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on link $2$
	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on link $1$ or $2$
\end{itemize}
Remember that we have assumed that $t_1 > t_2 \stackrel{\ref{lemma:latencies_tolls}}{\Leftrightarrow} \ell_1(x_1(t)) < \ell_2(x_2(t))$.
Therefore the flow in the lower-latency link $1$ has players with $\alpha(p) \le \as(t)$, while the flow in the higher-latency link $2$ has players with $\alpha(p) \ge \as(t)$.
Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
Alternative split labels could be rushed-relaxed or rich-poor.
\autoref{table:split_summary} provides of a summary of the properties for each part of the split

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^{|N|}|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	In the case of $N = [2]$ where there exists only one link pair, we will simply write $\as(t)$.
\end{definition}
We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money-sensitivity value.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

@@

At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering of the links.
In order to emphasise on this, let's restrict ourselves to $2$ links and point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
\[
	x(t_d) =
	\begin{cases*}
		x(t_d, 0) & $t_d \ge 0$ \\
		x(0, -t_d) & $t_d < 0$ \\
	\end{cases*}
\]
We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{|N| - 1}$.

With that in mind, we will investigate the monotonicity of $\as$ in relation to toll differences (and in extension to latency differences) and only when the ordering does not change.
For this we will need to compare different tolls that create lower-upper splits in the same links, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
We will capture this with the following condition
\begin{equation}
	\label{eq:split_property_cond_tolls_0}
	\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0
\end{equation}
where indeed if $t_i > t_j$ then
\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same toll ordering on links, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.

@@

The above show that $\as(t)$ is continuous for all $t \ne 0$, approaches $0$ at large toll differences and increases as that difference approaches $0$, thus making the side limits around $0$ have different values (apart from the very specific case where $x_1(0) = x_2(0)$).
We apply this on Example \ref{example:simple_alpha} to solidify this.
Since $\alpha$ is continuous we get from Corollary \ref{corollary:split_asymptotic_continuous} that
\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0)) = 4/3, \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) = 5/3\]

All the above give us the graph for $\as$ in Figure \ref{figure:alpha_simple:split_example}.
\begin{figure}
	\centering
	\begin{tikzpicture}[x=5cm, y=2cm, every node/.style={font=\small}]
		% Axes
		\draw[->] (0,0) -- (1.2,0) node[right] {$t_1$};
		\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

		% Tick marks
		\draw (0,0) -- (0,-0.05) node[below] {$0$};
		\draw (0.5,0) -- (0.5,-0.05) node[below] {$t_2$};
		\draw (0,4/3) -- (-0.05,4/3) node[left] {$4/3$};
		\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};

		% Function graph
		\draw[thick] (0,0.1) -- (0.5,4/3);
		\draw[thick] (0.5,5/3) -- (1,0.1);

		% Dots
		\fill[white] (0.5,4/3) ellipse (0.02 and 0.05);
		\draw[black] (0.5,4/3) ellipse (0.02 and 0.05);
		\fill[white] (0.5,5/3) ellipse (0.02 and 0.05);
		\draw[black] (0.5,5/3) ellipse (0.02 and 0.05);
	\end{tikzpicture}
	\caption{Split function of Example \ref{example:simple_alpha}}
	\label{figure:alpha_simple:split_example}
\end{figure}

@@

Having now a good overview of the overall values of $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
Do then those values actually affect our game in any way?
We answer this in the theorem below, which is the main result of this chapter, preceded by a lemma to describe those missing values.

\begin{lemma}
	\label{lemma:as_upper_bound}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
	For all $i, j \in N, i \ne j$ it holds that
	\[\as^{(i, j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
	%or equivalently if $\alpha$ continuous at $x_1(0)$ and $x_2(0)$
	%\[\as(t) \le \max\{\alpha(x_1(0)), \alpha(x_2(0))\}\]
\end{lemma}

@@

We can see how this theorem applies to Example \ref{example:simple_alpha}, where $\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3$.
Theorem \ref{theorem:alpha_upper_irrelevant} states that even if we used a distribution function such as
\[
	\alpha(p) =
	\begin{cases}
		p + 1 & p \le 2/3 \\
		p + 10 & p > 2/3
	\end{cases}
\]
then $\as$ would still behave the same way as those $(2/3, 1]$ players will always be in the upper split regardless of their $\alpha$ value.

This irrelevancy will become more apparent later when calculating best responses, as even in the pricing games those higher values are never used.
We finish this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
Note that since the behavior of a single player has no effect on the game, it doesn't suffice to assume $\alpha(0) = 0$ just for player $0$, so in order to capture the notion of having many players with $\alpha$ values close to $0$ we additionally assume that $0$ is an accumulation point in $\alpha$.
\begin{lemma}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
	Then $x_1(t) > 0, \forall t \in \R_+^{|N|}$
\end{lemma}

@@

@@

Intuitively, the above means that increasing the money sensitivity of all players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money-sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.

Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} leads us to the following one.
\begin{lemma}
	\label{lemma:a_fixed_c_relation}
	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
	Then the following are true
	\begin{enumerate}[$(i)$]
		%\item $x^{(1)}(0) = x^{(2)}(0)$
		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
	\end{enumerate}
\end{lemma}

@@

>>>>

The structure of this thesis is as such.
We finish this chapter by briefly presenting previous work in this field, all while examining some of the different models and properties that have been researched in the literature so far.
This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
This includes formal definitions of the models and properties we introduced from previous work, as well as some additional -but still basic- properties of the models, with heavy focus on the user's time-money trade-off, captured by a money sensitivity distribution function $\alpha$.

Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money sensitivity split}, which captures the notion of a (potentially non-existent) player whose money sensitivity makes them view the two links as equal.
We will then analyse that notion and provide properties and bounds for its values.
Finally, in the chapter's main result, we prove a general property of heterogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.

@@

Selfish routing is the study of trafficked networks where selfish users seek to optimise their own traffic cost.
The main interest is on instances where all users are content with the traffic they experience and no one wishes to change their strategy, a notion known as a Nash Equilibrium, or equivalently from the work of Wardrop \cite{wardrop_theoretical_1952}, a Wardrop Equilibrium.
Models from this field have been proven extremely useful in solving a variety of real-world problems in economics \cite{pigou1920economics}, transportation \cite{beckmann1956studies}, \cite{wardrop_theoretical_1952} and more, resulting in a vast history in the literature (see \cite{roughgarden2002sr} and \cite{roughgarden2005slpoa} for more references).
It has been well-established, at least as early as 1920 from the work of Pigou \cite{pigou1920economics}, that selfish behavior in congested networks can create (arbitrary) inefficiencies with regard to the total latency experienced by all users.
A long-standing practice to solve these inefficiencies has been to regulate the network by adding tolls to the links, thus altering the cost of the link usage.
A classical result on this is the use of marginal tolls (Beckman et al. \cite{beckmann1956studies}), where each link user is charged a toll corresponding to their externality, i.e. the added congestion effect caused by their participation in the network.
This technique can eradicate the inefficiencies and create optimal flow in the network, however it assumes a strong homogeneity among the users.
Marginal cost pricing has been investigated in networks with heterogeneous users (e.g. Dafermos \cite{dafermos1973toll}), with the resulting payment required by users on same links being different, an unwanted and non-practical approach, which also requires knowledge of the users' sensitivity beforehand.

Congestion games were formally introduced by Rosenthal \cite{Rosenthal1973ACO} who also proved that in those games a pure Nash Equilibrium always exists.
Later, Monterer-Shapely \cite{MONDERER1996124} defined the class of potential games (games where the incentive for all players to change their strategy can be expressed with a global function) and proved that congestion games are equivalent to exact potential games (potential games where a change in strategy from any player alter the potential function the exact way it alters the player's cost).
%One of the major contributions in this field has been the introduction of the Wardrop equilibrium \cite{wardrop_theoretical_1952}, a notion of Nash equilibrium for potential games, where the Wardrop principles provide a framework to describe and analyse those equilibria.
Milchtaich \cite{MILCHTAICH1996111} then investigated different pay-off functions for congestion games, where he showed that even though some best-reply strategies may end up in a cyclic path, there is always a path that leads to Nash equilibrium with pure strategies.

@@

In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different time-money trade-off values.
We describe this by adding a money sensitivity weight $\alpha(p)$ on the toll costs experienced by a player, making them see the cost of a link with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
By also assuming that the players are sorted by money sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
We call $\alpha$ a \textit{distribution function}.
Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
%Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.

@@

\section*{Summary}

In this chapter we will formalise and investigate the behaviour of the way a heterogeneous flow splits among the network links.
In order to tackle the variance in money sensitivity among the flow users, we will focus on two (arbitrary) links and seek a money sensitivity value for which, for a given set of tolls, the two link costs are equal.
After some discussion around the intuition of this idea, we will formally define a \textit{money sensitivity split} function (\ref{definition:split_function}) to capture this notion, as well as describe its essential idea of splitting the sensitivity values of the link's users to lower and higher values (Corollary \ref{corollary:split_to_alpha}).
A discussion will then be necessary about the set of sensitivity values in the flow users of a link which will lead us to defining them in \ref{definition:alpha_flow_sets}.
We then proceed with Lemmas to describe the split function's bounds (\ref{lemma:split_basic}), monotonicity (\ref{lemma:split_monotonicity}) and asymptotic behavior (\ref{lemma:split_asymptotic}), with which we'll arrive at the function's characterisation, cementing it visually for Example \ref{example:simple_alpha} in Figure \ref{figure:alpha_simple:split_example}.
Finally, some observations about the split function's global upper bounds (Lemma \ref{lemma:split_upper_bound}) will have as logical consequence this chapter's main result, Theorem \ref{theorem:alpha_upper_irrelevant}, which states that there may exist a portion of players whose sensitivity value can be arbitrarily high without affecting the network game.

@@

One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money sensitivity values, view toll values also differently, and therefore, in practice, play different games.
In the analysis of Example \ref{example:simple_alpha} we can find a first glimpse on how to tackle this issue, as we can see that the flow users on each link are organised around the player that views the two link costs as equal.
This notion will be the center of this chapter, and using it we will try and describe some properties about all users.

We start with a simple example in a network with $2$ links.
Consider $([2], \ell, \alpha)$, a heterogeneous parallel game with two links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
For the $2$ links of the game we introduce the term \textit{money sensitivity split} $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player views the $2$ links' total costs as equal.
More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
from which, after solving for $\as(t)$, we get
\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\\
Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
\begin{itemize}
	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) t_1 < \ell_2(x_2(t)) + \alpha(p) t_2$, so $p$ is on link $1$
	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) t_1 > \ell_2(x_2(t)) + \alpha(p) t_2$, so $p$ is on link $2$
	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) t_1 = \ell_2(x_2(t)) + \alpha(p) t_2$, so $p$ is either on link $1$ or $2$
\end{itemize}
Remember that we have assumed that $t_1 > t_2 \stackrel{\ref{lemma:latencies_tolls}}{\Leftrightarrow} \ell_1(x_1(t)) < \ell_2(x_2(t))$.
Therefore the flow in the lower-latency link $1$ has players with $\alpha(p) \le \as(t)$, while the flow in the higher-latency link $2$ has players with $\alpha(p) \ge \as(t)$.
Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
Alternative split labels could be rushed-relaxed or rich-poor.
\autoref{table:split_summary} provides of a summary of the properties for each part of the split

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^{|N|}|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	In the case of $N = [2]$ where there exists only one link pair, we will simply write $\as(t)$.
\end{definition}
We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money sensitivity value.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

@@

At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering on links.
With that in mind, we will investigate the monotonicity of $\as$ in relation to those toll differences (and in extension to latency differences) and only when the link ordering does not change.
For the latter condition to be true, we will need to compare different tolls that create lower-upper splits in the same links, or, in other words, for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$.
We will capture this with the following condition
\begin{equation}
	\label{eq:split_property_cond_tolls_0}
	\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0
\end{equation}
where indeed if $t_i > t_j$ then
\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same toll ordering on links, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.

@@

The above show that $\as(t)$ is continuous for all $t \ne 0$, approaches $0$ at large toll differences and increases as that difference approaches $0$, thus making the side limits around $0$ have different values (apart from the very specific case where $x_1(0) = x_2(0)$).
At this point we should also mention that at the toll difference bounds we discussed in Chapter \ref{chapter:preliminaries}, $\as$ takes the value of the least sensitive player, i.e. $\alpha(0)$.

We apply this on Example \ref{example:simple_alpha} to solidify this.
Since $\alpha$ is continuous we get from Corollary \ref{corollary:split_asymptotic_continuous} that
\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0)) = 4/3, \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) = 5/3\]
Toll difference bounds are $t_1 - t_2 \le 2$ and $t_2 - t_1 \le 1$.
The distribution function for this example is simple enough for us to also calculate a closed type for $\as(t)$ (included analytically in the \hyperref[chapter:appendix]{Appendix}), from which calculations we get
\[
	\as(t) =
	\begin{cases}
		\frac{1}{t_2 - t_1} & t_1 - t_2 \le -1 \\
		\frac{4}{3 + (t_2 - t_1)} & t_1 - t_2 \in (-1, 0) \\
		\frac{5}{3 + (t_1 - t_2)} & t_1 - t_2 \in (0, 2) \\
		\frac{2}{t_2 - t_1} & t_1 - t_2 \ge 2
	\end{cases}
\]
whose plot is in Figure \ref{figure:alpha_simple:split_example} and which confirms the analysis we did above.

\begin{figure}
	\centering
	\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
		% Axes
		\draw[->] (0,0) -- (-1.1,0);
		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
		\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

		% Tick marks
		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
		\draw (2,0) -- (2,-0.05) node[below] {$2$};
		\draw (0,2) -- (-0.05, 2) node[left] {$2$};
		\draw (0,4/3) -- (0.05,4/3) node[right] {$4/3$};
		\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
		\draw (0,1) -- (-0.05,1) node[left] {$1$};

		% Function graph
		%\draw[thick] (-1,1) -- (0,4/3);
		%\draw[thick] (0,5/3) -- (2,1);
		\draw[thick,samples at={-1,0}] plot (\x,{4/(3 - \x)});
		\draw[thick,samples at={0,2}] plot (\x,{5/(3 + \x)});

		% Dots
		\fill[white] (0,4/3) ellipse (0.03 and 0.03);
		\draw[black] (0,4/3) ellipse (0.03 and 0.03);
		\fill[white] (0,5/3) ellipse (0.03 and 0.03);
		\draw[black] (0,5/3) ellipse (0.03 and 0.03);
	\end{tikzpicture}
	\caption{Split function of Example \ref{example:simple_alpha}}
	\label{figure:alpha_simple:split_example}
\end{figure}

@@

Having now a good overview of the overall values of $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
Do those values actually affect our game in any way?
We answer this in the theorem below, which is the main result of this chapter, preceded by a lemma to describe those missing values.

\begin{lemma}
	\label{lemma:split_upper_bound}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
	For all $i, j \in N, i \ne j$ it holds that
	\[\as^{(i, j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
	%or equivalently if $\alpha$ continuous at $x_1(0)$ and $x_2(0)$
	%\[\as(t) \le \max\{\alpha(x_1(0)), \alpha(x_2(0))\}\]
\end{lemma}

@@

We can see how this theorem applies to Example \ref{example:simple_alpha}, where $\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3$.
Theorem \ref{theorem:alpha_upper_irrelevant} states that even if we used a distribution function such as
\[
	\alpha(p) =
	\begin{cases}
		p + 1 & p \le 2/3 \\
		\mathrm{e}^p & p > 2/3
	\end{cases}
\]
then $\as$ would still behave the same way as those $(2/3, 1]$ players will always be in the upper split regardless of their $\alpha$ value.

This irrelevancy will become more apparent later when calculating best responses, as even in the pricing games those higher values are never used.

@@

We start this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
Note that since the behavior of a single player has no effect on the game, it doesn't suffice to assume $\alpha(0) = 0$ just for player $0$, so in order to capture the notion of having many players with $\alpha$ values close to $0$ we additionally assume that $0$ is an accumulation point in $\alpha$.
\begin{lemma}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
	Then $x_1(t) > 0, \forall t \in \R_+^{|N|}$
\end{lemma}

@@

Intuitively, the above means that increasing the money sensitivity of all players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.

Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} leads us to the following proposition.
\begin{lemma}
	\label{lemma:a_fixed_c_relation}
	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
	Then the following are true
	\begin{enumerate}[$(i)$]
		%\item $x^{(1)}(0) = x^{(2)}(0)$
		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
	\end{enumerate}
\end{lemma}

@@

%Intuitively, the

		% Tick marks
		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
		\draw (-1/3,0) -- (-1/3,-0.05) node[below] {$-\frac13$};
		\draw (-1/4,0) -- (-1/4,-0.05) node[below] {$-\frac14$};
		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
		\draw (2/4,0) -- (2/4,-0.05) node[below] {$\frac12$};
		\draw (2/3,0) -- (2/3,-0.05) node[below] {$\frac23$};
		\draw (2,0) -- (2,-0.05) node[below] {$2$};
		\draw (0,1) -- (0.05,1) node[right] {$1$};
		\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
